### 2019-02-15 sections/intuition.tex
Fixed minor nit 10 from reviewer #3
add something about higher-order tasks

@@

The decision to move on to the next task is not taken by the task itself.
It is based on a calculation to determine the next tasks.
The step combinators in $t \Then e$ and $t \Next e$ pass the value of $t$ to the continuation $e$.
They both act like $t$ as long as the step is guarded.
Once it becomes unguarded, the task continues as $e\ v$, where $v$ is the observed value of $t$.
% The continuation $e$ is a function which calculates the next task or $\Fail$, signalling no continuation is present.
The task $t \Next e$ requires an input event $\Continue$ in addition to the step being unguarded. % in order to step.

>>>>

From a programmer's point of view,
tasks should not just model their real world equivalents.
They should be reusable units in a programming language.
Similar tasks should be specified once,
and reused in new context.
Taking this further,
by specifying tasks that take other tasks as arguments,
programmers can have a lot of freedom to create their own reusable collaboration patterns.
In other words,
programmers would like abstraction and higher-order tasks.

@@

The decision to move on to the next task is not taken by the task itself.
It is based on a calculation to determine the next tasks.
The step combinators in $t \Then e$ and $t \Next e$ pass the value of $t$ to the continuation $e$.
They both act like $t$ as long as the step is guarded.
Once it becomes unguarded, the task continues as $e\ v$, where $v$ is the observed value of $t$.
% The continuation $e$ is a function which calculates the next task or $\Fail$, signalling no continuation is present.
The task $t \Next e$ requires an input event $\Continue$ (Continue) in addition to the step being unguarded. % in order to step.
